\chapter{Methodology Analysis}
\justify
\quad 
 The users of both methodologies should have strong analytical skills, be able to work with large data sets, and have a good understanding of business objectives and requirements. They should also have a keen eye for detail, be able to think critically and creatively, and have excellent problem-solving skills. Effective communication skills are also important for presenting findings to stakeholders and decision-makers.

\section{User Characteristics}
\justify
\quad
\begin{itemize}
    \item \textbf{Prediction using Supervised ML:}The users of this methodology would typically have a background in data science, machine learning, and programming. They would have experience in working with data sets, cleaning and preprocessing data, selecting appropriate features, and building predictive models. They would also have knowledge of various ML algorithms, model selection, hyperparameter tuning, and evaluation metrics.
    \item \textbf{Data Science and Business Analytics:}The users of this methodology would typically have a background in data science, statistics, business intelligence, and analytics. They would have experience in working with different data sources, cleaning and transforming data, performing exploratory data analysis, selecting relevant features, and building predictive models. They would also have knowledge of various statistical methods, modeling techniques, and communication skills to present the findings effectively to stakeholders.
  
\end{itemize}

\section{Overview of Functional Requirements}
\justify
\quad
\begin{itemize}
    \item \textbf{Data ingestion:}The system should be able to ingest data from various sources such as databases, files, or APIs.
    \item \textbf{Data preprocessing:}The system should be able to preprocess data by cleaning, transforming, and normalizing it.
    \item \textbf{Exploratory data analysis: }The system should provide tools for visualizing and exploring data.
    \item \textbf{Feature engineering: }The system should provide feature engineering tools for selecting relevant features, reducing dimensionality, and engineering new features.
    \item \textbf{Statistical analysis:}The system should provide a range of statistical methods for analyzing data.
    \item \textbf{Model selection and training: }The system should provide a range of ML algorithms for model selection and training.
    \item \textbf{Model evaluation:  }The system should provide evaluation metrics for evaluating the performance of the model.
    \item \textbf{Model deployment:} The system should provide tools for deploying the trained model in production environments.
    \item \textbf{Communication: } The system should provide tools for presenting findings to stakeholders through dashboards, reports, and visualizations.


\end{itemize}

\newpage