\chapter{Introduction}
\justify
\quad 


\section{Objectives}
\justify 
\quad 
The objective of the Data Science and Business Analytics internship is to provide students with practical experience in applying data science and business analytics concepts and techniques in real-world settings. By participating in this internship, students will be able to:

Develop their technical skills in using analytical tools and techniques.
Gain practical experience in analyzing and interpreting real-world data sets.
Understand the role of data-driven insights in making informed business decisions.
Enhance their communication and collaboration skills by presenting findings and recommendations to stakeholders.
Participate in data-driven projects and collaborate with other team members.
Engage in training and professional development activities to further their understanding of the field.
Gain a deeper understanding of the career opportunities available in the field of data science and business analytics.


\section{Scope}
The internship program typically includes the following scope:
\begin{itemize}
\item \textbf{Data Collection and Pre-processing} : The interns will be exposed to the process of collecting, cleaning, and preparing data for analysis.
\item \textbf{Data Analysis} :The interns will work on analyzing data using various statistical and machine learning techniques to derive insights and patterns from the data.
\item \textbf{Data Visualization and Communication} : Write description of the point here.
\item \textbf{Business Applications} : The interns will work on real-world projects and gain an understanding of how data-driven insights can be used to solve business problems.
\item \textbf{Professional Development} : The interns will have access to various training sessions and workshops to enhance their skills in data science and business analytics.

\end{itemize}


\newpage


